### 2017-02-26 2017mergingmerges/section/XX-Processes.tex
Sort out terminology, process, machine, combinator, operator

Next, the instruction @(case (f || (l /= v)) A2 {} A3 {})@ checks whether the predicate @(f || (l /= v))@ is true; if so it proceeds to the instruction at label @A2@, otherwise it proceeds to the instruction at label @A3@. We use the variable @l@ (last) to track the last value read from the stream, and the boolean @f@ (first) to track whether this is the first element.

>>>>

Next, the instruction @(case (f || (l /= v)) A2 {} A3 {})@ checks whether predicate @(f || (l /= v))@ is true; if so it proceeds to the instruction at label @A2@, otherwise it proceeds to @A3@. We use the variable @l@ (last) to track the last value read from the stream, and the boolean @f@ (first) for whether this is the first element.
